Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-12 paper/main.tex
manuscript works with tex file for newcommands
replace placeholders in table to commands

\begin{document}
\input{descr-stats-ao-events.tex}
\input{descr-stats-av-events.tex}

@@

\todo[inline]{aus Speech-Anno Paper 'descriptive-statistics-anno.py' übernehmen \& anpassen, um Statistiken und runcommand-file zu erstellen}

@@

% noun categorization
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
The nouns were categorized by the clue they provide about the cinematographic
scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
persons (female, female name; male, male name, person), a person's appearance
(face, head; body, bodypart), and a scene's inherent objects (object,
furniture). See Table \ref{tab:descr-nouns} for a complete overview of all
cateogries [+++rules, counts, examples].

@@

% Tabelle der Descriptive Nouns;
\todo[inline]{decr-stats-anno.py; Schrägstriche vor Platzhalter}

\todo[inline]{Caption hübsch machen}
    \caption{Narrator's descriptive nouns.
        All categories sorted alphapetically.
    Examples are given in English.}
\label{tab:descr-nouns}
\begin{tabular}{llllllllllll}
\textbf{category} & \textbf{rule} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & aDescrBodyAll & aDescrBodyI & aDescrBodyII & aDescrBodyIII & aDescrBodyIV & aDescrBodyV & aDescrBodyVI & aDescrBodyVII & aDescrBodyVIII \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe & aDescrBodypartAll & aDescrBodypartI & aDescrBodypartII & aDescrBodypartIII & aDescrBodypartIV & aDescrBodypartV & aDescrBodypartVI & aDescrBodypartVII & aDescrBodypartVIII \tabularnewline
face & face or parts of it & face, ear, nose, mouth & aDescrFaceAll & aDescrFaceI & aDescrFaceII & aDescrFaceIII & aDescrFaceIV & aDescrFaceV & aDescrFaceVI & aDescrFaceVII & aDescrFaceVIII \tabularnewline
female & female person & nurse, mother, woman & aDescrFemaleAll & aDescrFemaleI & aDescrFemaleII & aDescrFemaleIII & aDescrFemaleIV & aDescrFemaleV & aDescrFemaleVI & aDescrFemaleVII & aDescrFemaleVIII \tabularnewline
females & female persons & women & aDescrFemalesAll & aDescrFemalesI & aDescrFemalesII & aDescrFemalesIII & aDescrFemalesIV & aDescrFemalesV & aDescrFemalesVI & aDescrFemalesVII & aDescrFemalesVIII \tabularnewline
fname & female name & Jenny & aDescrFnameAll & aDescrFnameI & aDescrFnameII & aDescrFnameIII & aDescrFnameIV & aDescrFnameV & aDescrFnameVI & aDescrFnameVII & aDescrFnameVIII \tabularnewline
furniture & movable objects insides/outsides & bench, bed, table, chair & aDescrFurnitureAll & aDescrFurnitureI & aDescrFurnitureII & aDescrFurnitureIII & aDescrFurnitureIV & aDescrFurnitureV & aDescrFurnitureVI & aDescrFurnitureVII & aDescrFurnitureVIII \tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & aDescrGeoAll & aDescrGeoI & aDescrGeoII & aDescrGeoIII & aDescrGeoIV & aDescrGeoV & aDescrGeoVI & aDescrGeoVII & aDescrGeoVIII \tabularnewline
geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & aDescrGeoroomAll & aDescrGeoroomI & aDescrGeoroomII & aDescrGeoroomIII & aDescrGeoroomIV & aDescrGeoroomV & aDescrGeoroomVI & aDescrGeoroomVII & aDescrGeoroomVIII \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & aDescrHeadAll & aDescrHeadI & aDescrHeadII & aDescrHeadIII & aDescrHeadIV & aDescrHeadV & aDescrHeadVI & aDescrHeadVII & aDescrHeadVIII \tabularnewline
male & male person & man, father, soldier & aDescrMaleAll & aDescrMaleI & aDescrMaleII & aDescrMaleIII & aDescrMaleIV & aDescrMaleV & aDescrMaleVI & aDescrMaleVII & aDescrMaleVIII \tabularnewline
males & male persons & boys, opponents & aDescrMalesAll & aDescrMalesI & aDescrMalesII & aDescrMalesIII & aDescrMalesIV & aDescrMalesV & aDescrMalesVI & aDescrMalesVII & aDescrMalesVIII \tabularnewline
mname & male name & Bubba, Kennedy & aDescrMnameAll & aDescrMnameI & aDescrMnameII & aDescrMnameIII & aDescrMnameIV & aDescrMnameV & aDescrMnameVI & aDescrMnameVII & aDescrMnameVIII \tabularnewline
object & countable entity with firm boundarie & telephone, car & aDescrObjectAll & aDescrObjectI & aDescrObjectII & aDescrObjectIII & aDescrObjectIV & aDescrObjectV & aDescrObjectVI & aDescrObjectVII & aDescrObjectVIII \tabularnewline
objects & countable entities with firm boundaries &  wheels, photos & aDescrObjectsAll & aDescrObjectsI & aDescrObjectsII & aDescrObjectsIII & aDescrObjectsIV & aDescrObjectsV & aDescrObjectsVI & aDescrObjectsVII & aDescrObjectsVIII \tabularnewline
persons & concrete persons of unknown sex / gender & hippies, patients & aDescrPersonsAll & aDescrPersonsI & aDescrPersonsII & aDescrPersonsIII & aDescrPersonsIV & aDescrPersonsV & aDescrPersonsVI & aDescrPersonsVII & aDescrPersonsVIII \tabularnewline
setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' & aDescrSettingnewAll & aDescrSettingnewI & aDescrSettingnewII & aDescrSettingnewIII & aDescrSettingnewIV & aDescrSettingnewV & aDescrSettingnewVI & aDescrSettingnewVII & aDescrSettingnewVIII \tabularnewline
setting\_rec & recurring setting & at the ``bus stop'' & aDescrSettingrecAll & aDescrSettingrec & aDescrSettingrecII & aDescrSettingrecIII & aDescrSettingrecIV & aDescrSettingrecV & aDescrSettingrecVI & aDescrSettingrecVII & aDescrSettingrecVIII \tabularnewline
++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' &  aDescrAll & aDescrI & aDescrII & aDescrIII & aDescrIV & aDescrV & aDescrVI & aDescrVII & aDescrVIII \tabularnewline

@@

At the first level analyzing each segment for every subject, we created
regressors for the AO data from the narrator's descriptive nouns (see Table
\ref{tab:descr-nouns}) added to the annotation of speech
\citep{haeusler2020speechanno}. For the AV stimulus, we created regressors from
events provided by an annotation of movie cuts and depicted locations
\citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
First, both annotations were split into eight parts corresponding to the eight
segments used as stimuli during fMRI scanning.

>>>>

\begin{document}
\input{descr-stats-ao-events.tex}
\input{descr-stats-av-events.tex}
\input{descr-stats-anno.tex}

@@

\todo[inline]{um Hinweis bzgl. AV ergänzen}

@@

% noun categorization
% Kategorie ``++'' enthält ausnahmesweise auch adverbiale Best. der Zeit.
The nouns were categorized by the clue they provide about the cinematographic
scene's environment (geo, geo-room; setting\_new, setting\_old), its inherent
persons (female, female name; male, male name, person), a person's appearance
(face, head; body, bodypart), and a scene's inherent objects (object,
furniture). See Table \ref{tab:descr-nouns-counts} for a complete overview of all
cateogries [+++rules, counts, examples].

@@

\begin{table*}[t]
    \caption{Narrator's descriptive nouns.
        All categories sorted alphapetically.
    Examples are given in English.}
\label{tab:descr-nouns-count}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress
shirt \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

% Tabelle der Descriptive Nouns;
\todo[inline]{Caption hübsch machen}

\begin{table*}[t]
    \caption{Narrator's descriptive nouns.
        All categories sorted alphapetically.
    Examples are given in English.}
\label{tab:descr-nouns-count}
\begin{tabular}{llllllllllll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} & \textbf{all} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} & \textbf{5} & \textbf{6} & \textbf{7} & \textbf{8} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress shirt & \anBodyAll & \anBodyI & \anBodyII & \anBodyIII & \anBodyIV & \anBodyV & \anBodyVI & \anBodyVII & \anBodyVIII \tabularnewline

bodypart & limbs and trousers & arm, finger, leg, toe & \anBodypartAll & \anBodypartI & \anBodypartII & \anBodypartIII & \anBodypartIV & \anBodypartV & \anBodypartVI & \anBodypartVII & \anBodypartVIII \tabularnewline

face & face or parts of it & face, ear, nose, mouth & \anFaceAll & \anFaceI & \anFaceII & \anFaceIII & \anFaceIV & \anFaceV & \anFaceVI & \anFaceVII & \anFaceVIII \tabularnewline

female & female person & nurse, mother, woman & \anFemaleAll & \anFemaleI & \anFemaleII & \anFemaleIII & \anFemaleIV & \anFemaleV & \anFemaleVI & \anFemaleVII & \anFemaleVIII \tabularnewline

females & female persons & women & \anFemalesAll & \anFemalesI & \anFemalesII & \anFemalesIII & \anFemalesIV & \anFemalesV & \anFemalesVI & \anFemalesVII & \anFemalesVIII \tabularnewline

fname & female name & Jenny & \anFnameAll & \anFnameI & \anFnameII & \anFnameIII & \anFnameIV & \anFnameV & \anFnameVI & \anFnameVII & \anFnameVIII \tabularnewline

furniture & movable objects insides/outsides & bench, bed, table, chair & \anFurnitureAll & \anFurnitureI & \anFurnitureII & \anFurnitureIII & \anFurnitureIV & \anFurnitureV & \anFurnitureVI & \anFurnitureVII & \anFurnitureVIII \tabularnewline

geo & immobile landmarks & building, tree, street, alley, meadow, cornfield, river & \anGeoAll & \anGeoI & \anGeoII & \anGeoIII & \anGeoIV & \anGeoV & \anGeoVI & \anGeoVII & \anGeoVIII \tabularnewline

geo-room & rooms / locales; elements defining a locale's spatial layout & living room; wall, door, window, floor, turf & \anGeoroomAll & \anGeoroomI & \anGeoroomII & \anGeoroomIII & \anGeoroomIV & \anGeoroomV & \anGeoroomVI & \anGeoroomVII & \anGeoroomVIII \tabularnewline

head & non-face parts of the head; worn headgear & head, hair, ear, neck, helmet & \anHeadAll & \anHeadI & \anHeadII & \anHeadIII & \anHeadIV & \anHeadV & \anHeadVI & \anHeadVII & \anHeadVIII \tabularnewline

male & male person & man, father, soldier & \anMaleAll & \anMaleI & \anMaleII & \anMaleIII & \anMaleIV & \anMaleV & \anMaleVI & \anMaleVII & \anMaleVIII \tabularnewline

males & male persons & boys, opponents & \anMalesAll & \anMalesI & \anMalesII & \anMalesIII & \anMalesIV & \anMalesV & \anMalesVI & \anMalesVII & \anMalesVIII \tabularnewline

mname & male name & Bubba, Kennedy & \anMnameAll & \anMnameI & \anMnameII & \anMnameIII & \anMnameIV & \anMnameV & \anMnameVI & \anMnameVII & \anMnameVIII \tabularnewline

object & countable entity with firm boundarie & telephone, car & \anObjectAll & \anObjectI & \anObjectII & \anObjectIII & \anObjectIV & \anObjectV & \anObjectVI & \anObjectVII & \anObjectVIII \tabularnewline

objects & countable entities with firm boundaries &  wheels, photos & \anObjectsAll & \anObjectsI & \anObjectsII & \anObjectsIII & \anObjectsIV & \anObjectsV & \anObjectsVI & \anObjectsVII & \anObjectsVIII \tabularnewline

persons & concrete persons of unknown sex / gender & hippies, patients & \anPersonsAll & \anPersonsI & \anPersonsII & \anPersonsIII & \anPersonsIV & \anPersonsV & \anPersonsVI & \anPersonsVII & \anPersonsVIII \tabularnewline

setting\_new & setting mentioned for the first time &  on a ``bridge'', on an ``alley'', on ``campus'' & \anSettingnewAll & \anSettingnewI & \anSettingnewII & \anSettingnewIII & \anSettingnewIV & \anSettingnewV & \anSettingnewVI & \anSettingnewVII & \anSettingnewVIII \tabularnewline

setting\_rec & recurring setting & at the ``bus stop'' & \anSettingrecAll &
\anSettingrecI & \anSettingrecII & \anSettingrecIII & \anSettingrecIV & \anSettingrecV & \anSettingrecVI & \anSettingrecVII & \anSettingrecVIII \tabularnewline
++ & nouns, adverbial adjectives and adverbs & in the ``evening'', it's ``daytime'', ``later'' &  anAll & \anI & \anII & \anIII & \anIV & \anV & \anVI & \anVII & \anVIII \tabularnewline
aDescrV & aDescrVI & aDescrVII & aDescrVIII \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

@@

At the first level analyzing each segment for every subject, we created
regressors for the AO data from the narrator's descriptive nouns (see Table
\ref{tab:descr-nouns-counts}) added to the annotation of speech
\citep{haeusler2020speechanno}. For the AV stimulus, we created regressors from
events provided by an annotation of movie cuts and depicted locations
\citep{haeusler2016cutanno}.
% https://github.com/psychoinformatics-de/studyforrest-data-annotations/blob/master/code/researchcut2segments.py}
First, both annotations were split into eight parts corresponding to the eight
segments used as stimuli during fMRI scanning.
